Self Regulation Ontology Retest Data Report

### 2017-03-20 SRO_Report.Rmd
working on new report

```{r}
tst_mng_cln <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/meaningful_variables_clean.csv')

rtst_mng_cln <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/meaningful_variables_clean.csv')

names(rtst_mng_cln)[which(names(rtst_mng_cln) %in% names(tst_mng_cln) == FALSE)]

names(tst_mng_cln)[which(names(tst_mng_cln) %in% names(rtst_mng_cln) == FALSE)]
```

@@

```{r}
library(psych)
sf <- matrix(c(9,    2,   5,    8,
6,    1,   3,    2,
8,    4,   6,    8,
7,    1,   2,    6,
10,   5,   6,    9,
6,   2,   4,    7),ncol=4,byrow=TRUE)
colnames(sf) <- paste("J",1:4,sep="")
rownames(sf) <- paste("S",1:6,sep="")
sf
ICC(sf)
```

```{r}
library('irr')

time1 <- c(0:10)
time2 <- c(1:11)
times <- cbind(time1,time2)
rm(time1, time2)
times
```

```{r}
icc(times,model = "twoway",
    type = "consistency",
    unit = "single",
    r0 = 0,
    conf.level = 0.95)
```

```{r}
#>>ICC=1 for consistency

icc(times,model = "twoway",
    type = "agreement",
    unit = "single",
    r0 = 0,
    conf.level = 0.95)
```

@@

```{r}
match_t1_t2 <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var)
  df = df %>% 
    gather(time, score, -sub_id) %>%
    separate(time, c("dv","drop","time"), sep="[.]") %>%
    select(-drop)%>%
    mutate(time=ifelse(time=="x",1,2))
  return(df)
}

tmp = match_t1_t2("adaptive_n_back.mean_load")

summary(lmer(score ~ (1|sub_id)+factor(time),data=tmp))

```

```{r}
summary(aov(score ~ factor(time) + Error(sub_id),tmp))
```

@@

>>>>

@@

@@

```{r}
match_t1_t2 <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var)
  df = df %>% 
    na.omit()%>%
    gather(time, score, -sub_id) %>%
    separate(time, c("dv","drop","time"), sep="[.]") %>%
    select(-drop)%>%
    mutate(time=ifelse(time=="x",1,2))
  return(df)
}

tmp = match_t1_t2("adaptive_n_back.mean_load") 
summary(aov(score~Error(sub_id)+time,tmp))
(0.692-((0.876*1+0.092*133)/134))/(0.692 + ((2-1)*((0.876*1+0.092*133)/134))) #ICC(1,1) ?
(0.692-0.092)/(0.692+ ((2-1)*0.092)+ ((2*(0.876-0.092))/134)) #ICC(2,1)
(0.692-0.092)/(0.692+((2-1)*0.092)) #ICC(3,1)
(0.692-((0.876*1+0.092*133)/134))/(0.692) #ICC(1,k)
(0.692-0.092)/(0.692+((2*(0.876-0.092))/134)) #ICC(2,k)
(0.692-0.092)/(0.692) #ICC(3.k)
sqrt((92.1+0.88+12.29)/133) #sd?
sd(tmp$score) #sd?
sqrt(0.092) #sem (smaller the better)
tmp = tmp %>% spread(time, score) %>% select(-dv, -sub_id)
ICC(tmp)

tmp = match_t1_t2("bis_bas_survey.BIS") 
summary(aov(score~Error(sub_id)+time,tmp))
# summary(aov(score~Error(sub_id/time)+time,tmp)) #same thing
sqrt(0.0477)
tmp = tmp %>% spread(time, score) %>% select(-dv, -sub_id)
ICC(tmp)
```

@@

Based on Weir 2005 ICC(3,k) does not take in to account within subject differences between two time points (fixed effect/systematic error by time). Thus, it is well approximated by Pearson's r and subject to similar criticisms. So if you're going to use this you should at least that this effect is not significant for a measure.

Conclusion based on Weir:
get ICC(3,k)
report effect size of time (p value and partial eta squared)
get SEM (sqrt(MS_error))
